---
title: "Differential eqution solving"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Package deSolve

```{r}
vdpol <- function (t, y, mu) {list(c(y[2],mu * (1 - y[1]^2) * y[2] - y[1]))}

library(deSolve)

yini <- c(y1 = 2, y2 = 0)
stiff <- ode(y = yini, func = vdpol,times = 0:3000, parms = 1000)
nonstiff <- ode(y = yini, func = vdpol,times = seq(0, 30, by = 0.01),parms = 1)
head(stiff, n = 3)
```

FULLY REP

```{r}
plot(stiff, type = "l", which = "y1",lwd = 2, ylab = "y",main = "IVP ODE, stiff")
```

FULLY REP

```{r}
plot(nonstiff, type = "l", which = "y1",lwd = 2, ylab = "y",main = "IVP ODE, nonstiff")
```

FULLY REP

# bvpSolve

```{r, error=T}
Prob14 <- function(x, y, xi)  {list(c(y[2],1/xi * (y[1] - (xi*pi*pi+1) * cos(pi*x))))}

library(bvpSolve)
x <- seq(-1, 1, by = 0.01)
shoot <- bvpshoot(yini = c(0, NA),yend = c(0, NA), x = x, parms = 0.01,func = Prob14)
twp <- bvptwp(yini = c(0, NA), yend = c(0,NA), x = x, parms = 0.0025,func = Prob14)
coll <- bvpcol(yini = c(0, NA),yend = c(0, NA), x = x, parms = 1e-04,func = Prob14)
```

NOT REP, package bvpSolve cannot be installed.

# Benchmark

```{r}
daefun<-function(t, y, dy, parms) {
  res1 <- - dy[1] - 0.04 * y[1] +1e4 * y[2] * y[3]
  res2 <- - dy[2] + 0.04 * y[1] -1e4 * y[2] * y[3] - 3e7 * y[2]^2
  res3 <- y[1] + y[2] + y[3] - 1
  list(c(res1, res2, res3),
       error = as.vector(y[1] + y[2] + y[3]) - 1)}
yini  <- c(y1 = 1, y2 = 0, y3 = 0)
dyini <- c(-0.04, 0.04, 0)
times <- 10 ^ seq(-6,6,0.1)

print(system.time(out <-daspk(y = yini,
                              dy = dyini,
                              times = times, res = daefun,
                              parms = NULL)))
```

FULLY REP, time of reprodution is of course shorter.

```{r}
plot(out, ylab = "conc.", xlab = "time",type = "l", lwd = 2, log = "x")
mtext("IVP DAE", side = 3, outer = TRUE,line = -1)
```

MOSTLY REP, the error plot is different, but the tendency is the same.

# ReacTran

```{r}
library(ReacTran)
Grid <- setup.grid.1D(N = 1000, L = 10)

pde1D <-function(t, C, parms)  {
  tran <- tran.1D(C = C, D = D,C.down = Cext, dx = Grid)$dC
  list(tran - Q) }

D   <- 1  
Q   <- 1  
Cext <- 20
```

FULLY REP, no errors while loading.

# RootSolve

```{r}
library(rootSolve)
print(system.time(std <- steady.1D(y = runif(Grid$N), func = pde1D, parms = NULL, nspec = 1)))
```

FULLY REP, produced in no time.

```{r}
plot (Grid$x.mid, std$y, type = "l",lwd = 2, main = "steady-state PDE", xlab = "x", ylab = "C", col = "red")
```

FULLY REP

```{r}
analytical <- Q/2/D*(Grid$x.mid^2 - 10^2) + Cext
max(abs(analytical - std$y))
```

FULLY REP

```{r}
require(deSolve)
times <- seq(0, 100, by = 1)
system.time(out <- ode.1D(y = rep(1, Grid$N),times = times, func = pde1D,parms = NULL, nspec = 1))
```

FULLY REP, it was of course reproduced faster.

```{r}
tail(out[, 1:4], n = 3)
```

FULLY REP

```{r}
image(out, xlab = "time, days",ylab = "Distance, cm",main = "PDE", add.contour = TRUE)
```

MOSTLY REP, colours a little bit brighter and more intensive.
