---
title: "pmml"
author: "Michał Wdowski"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})

knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# pmml

`pmml` is a package coming from [June 2009 R Journal issue](https://journal.r-project.org/archive/2009/RJ-2009-010/). It introduces an XML-based syntax for predictive models. Last update comes from 22nd April 2020.

```{r}
library(pmml)
library(rpart)
data(iris)

my.rpart <- rpart(Species ~ ., data=iris)
my.rpart
```
**FULLY REP**

```{r, output.lines=10}
pmml(my.rpart)
```
I assume that it is **FULLY REP**, altough the full output can't be seen in the original article.

```{r}
library(kernlab)
audit <- read.csv(file("http://rattle.togaware.com/audit.csv"))
```
**FULLY REP**

```{r}
myksvm <- ksvm(as.factor(TARGET_Adjusted) ~ ., data=audit[,c(2:10,13)], kernel = "rbfdot", prob.model=TRUE)
```
**HAD TO CHANGE STH**
Column `TARGET_Adjusted` was originally called `Adjusted`.

```{r, output.lines=10}
pmml(myksvm, data=audit)
```
I assume that it is **FULLY REP**, altough the full output can't be seen in the original article.


